Growth of the South African Economy:\\An Empirical Evaluation

### 2014-10-08 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Better definition of data source.

<<data, echo=FALSE, message=FALSE>>=
# Load historical data
historicalData <- SUN # From the EconData package

@@

# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "SUN", kind = "coeffs", dir=pp_path)
coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "SUN", kind = "fitted", dir=pp_path)
fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
# Load the original models.
oModels <- loadPostProcessedData(Source = "SUN", kind = "models", dir=pp_path)
oModels_ZA <- oModels$SUN$ZA
@

>>>>

<<data, echo=FALSE, message=FALSE>>=
# Load historical data
historicalData <- SUN # From the EconData package
sourceOfData <- "SUN"

@@

# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = sourceOfData, kind = "coeffs", dir=pp_path)
coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = sourceOfData, kind = "fitted", dir=pp_path)
fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
# Load the original models.
oModels <- loadPostProcessedData(Source = sourceOfData, kind = "models", dir=pp_path)
oModels_ZA <- oModels$SUN$ZA
@
